### 2025-05-11 paper/sections/introduction.tex
fix github link

All code implementations, including the models and experimental setups employed in this study, are publicly available on GitHub:\footnote{\url{https://github.com/YNWA-PZ/SemEval2025-task11}}. This repository provides full documentation of our methodologies, experimental results, and final model architectures.

>>>>

All code implementations, including the models and experimental setups employed in this study, are publicly available on GitHub:\footnote{\href{https://github.com/YNWA-PZ/SemEval2025-task11}{https://github.com/YNWA-PZ/SemEval2025-task11}}. This repository provides full documentation of our methodologies, experimental results, and final model architectures.
